How young children integrate information sources to infer the meaning of words

### 2020-10-23 paper/manuscript.Rmd
prep for submission

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,*"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "manuel_bohn@eva.mpg.de"
  - name          : "Michael Henry Tessler"
    affiliation   : "2,*"
  - name          : "Megan Merrick"
    affiliation   : "3"
  - name          : "Michael C. Frank"
    affiliation   : "3"

affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
  - id            : "2"
    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
  - id            : "3"
    institution   : "Department of Psychology, Stanford University"
  - id            : "*"
    institution   : "These authors contributed equally to this work"

abstract: |
  Before formal education begins, children typically acquire a vocabulary of thousands of words. This learning process requires the use of many different information sources in their social environment, including their current knowledge state as well as the context in which they hear words used. How is this information integrated? We specify a model according to which children consider all available information sources and integrate them via Bayesian inference. This model accurately predicted 2-to-5 year-old children’s word learning across a range of experimental conditions. Model comparison suggests that the integration process is stable across development and that the main locus of development is an increased sensitivity to individual information sources. We present a quantitative developmental theory of information integration for language learning, embedded in a larger framework that grounds language use and learning in social cognition.

keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling, common ground"
wordcount         : "X"

@@

Human communicative communicative abilities are unrivaled in the animal kingdom [@taylor2016language; @tomasello2008origins; @fitch2010evolution]. Language - in whatever modality - is the medium that allows humans to collaborate and coordinate in species-unique ways, making it the bedrock of human culture and society [@smith1997major]. Thus, in order to absorb the culture around them and become functioning members of a society, children need to learn language [@tomasello2018natural]. A central problem in language learning is referent identification: to learn the conventional symbolic relation between a word and an object, a child has to determine the intended referent of the word. Referents can only be identified in an inferential manner by reasoning about the speaker’s intentions [@bohn2019pervasive; @bruner1983child; @clark2009first; @tomasello2009constructing]. That is, the child has to infer what the speaker is communicating about based on information sources in the social context of the utterance.

From early on in development, children use a number of different mechanisms to harness such social-contextual information sources [@bohn2019pervasive; @clark2009first; @bloom2002children]. For example, children expect speakers to use novel words for unknown objects [@clark1987principle; @markman1988children; @carey1978acquiring; @halberda2003development], to talk about objects that are relevant [@frank2014inferring; @schulze20133], new in context [@akhtar1996role; @diesendruck2004two], or related to the ongoing conversation [@bohn_le_peloquin_koymen_frank_2020; @sullivan2016discourse; @horowitz2015young]. These different mechanisms, however, have largely been described and theorized about in isolation. The picture of the learning process that emerges is that of a “bag of tricks”: mechanisms that operate (and develop) independently from one another [@bloom2002children]. As such, this view of the learning process does not capture the complexity of natural social interaction during which many sources of information are present [@bergelson2017nature; @frank2013social]. Theses sources need to be integrated in order to accurately infer a speaker's intention.

When information integration is studied directly, the focus is mostly on how children interpret an ambiguous referring expression in light of social-contextual information [@ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers]. In one of these studies [@nadig2002evidence], children faced a 2 x 2 display with a ball, a pen and two glasses in it. The speaker, sitting on the opposite side of the display, saw only 3 of the compartments: the ball, the pen, and one of the glasses. When the speaker asked for "the glass", children had to integrate the semantics of the utterance with the perspective of the speaker to correctly infer which of the glasses - from their perspective - the speaker was referring to. This study, along with others, found that preschoolers use both information sources. What these studies do not do, however, is specify the process by which children integrate the different information sources. When discussing their results, authors refer to social-pragmatic theories of language use and learning [@grice1991studies; @sperber2001relevance; @clark1996using; @clark2009first; @tomasello2009constructing], all of which assume that information is integrated as part of a social inference process, but none of which clearly defines the process. As a consequence, we have no explicit and quantitative theory of how different information sources (and word learning mechanisms) are integrated.

We present a theory of this integration process. Following social-pragmatic theories of language learning [@clark2009first; @tomasello2009constructing], our theory is based on the following premises: information sources serve different functional roles, all part of an integrated social inference process [@clark1996using; @grice1991studies; @shafto2012learning; @sperber2001relevance]. Children use all available information to make inferences about the intentions behind a speaker’s utterance, which then leads them to correctly identify referents in the world and learn conventional word–object mappings. We formalize the computational steps that underlie this inference process in a cognitive model [@frank2012predicting; @goodman2016pragmatic; @oberauer2019addressing]. In the remainder of this paper, we rigorously test this theory by asking how well it serves the two purposes of any psychological theory: prediction and explanation [@shmueli2010explain; @yarkoni2017choosing]. First, we use the model to make quantitative predictions about children's behavior in new situations - predictions we test against new data. Next, we test how well the model explains the integration process by comparing it to alternative models that make different assumptions about *whether* information is integrated, *how* it is integrated and how the integration process *develops*.

We focus on three information sources that play an integral part in theorizing about language use and learning: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle; @sperber2001relevance], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using; @clark2015common], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children]. These information sources operate on different timescales: while (1) is a momentary expectation about a particular utterance, (2) grows over the course of a conversation, and (3) is learned across development. This interplay of timescales has been hypothesized to be an important component of word meaning inference [@frank2009using; @mcmurray2012word].

Our *rational integration model* arbitrates between information sources via Bayesian inference (see Fig. 1f for model formula). A listener ($L_{1}$) reasons about the referent of a speaker's ($S_{1}$) utterance. This reasoning is contextualized by the prior probability of each referent $\rho$ -- which we take to be a function of the common ground shared between the listener and the speaker. To decide between referents, the listener ($L_{1}$) reasons about what a rational speaker ($S_{1}$) with informativeness $\alpha$ would say given an intended referent. This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one. The informativity of each utterance is given by imagining which referent a listener, who interprets words according to their literal semantics (what we call a literal listener, $L_{0}$), would infer upon hearing the utterance. Naturally, this reasoning depends on what kind of semantic knowledge (for object j) $\theta$~j~ the speaker ascribes to the (literal) listener. Taken together, this model provides a quantitative theory of information integration during language learning. Furthermore, the model presents an explicit and substantive theory of development. It assumes that, while children’s sensitivity to the individual information sources increases with age, the way integration proceeds remains constant [@bohn2019pervasive; @bohn_tessler_merrick_frank_2019]. In the model, this is accomplished by making the parameters capturing sensitivity to speaker informativeness ($\alpha$~i~, Fig. 1d), the common ground ($\rho$~i~, Fig. 1c), and object specific semantic knowledge ($\theta$~i,j~, Fig. 1e) a function of the child’s age.

```{r fig1, include = T, fig.align = "center", fig.cap = "Experimental task and model. (a and b) Screenshots from the experimental task. (i) The speaker encounters one object and then leaves the scene (ii). While the speaker is away, a second object appears (iii), when returning, the speaker uses a novel word to request an object (iv). Sections (i) to (iii) establish common ground between the speaker and the listener, in that one object is new in context (green). The request in (iv) licenses an inference based on expectations about how informative speakers are (red). Listeners' semantic knowledge enters the task because the identity of the  known object on one of the tables is varied from well-known objects like a duck to relatively unfamiliar objects like a chess pawn (total of 12 objects - blue). (a) shows the condition in which common ground information is congruent (i.e. point to the same object) with speaker informativeness and (b) shows the incongruent condition. The congruent and incongruent conditions are each paired with the 12 known objects, resulting in 24 unique conditions. (c to e) show developmental trajectories for each information source, estimated from separate experiments (see supplement). (f) gives the model equation for the rational integration model and links information sources to model parameters.", out.width="100%"}
knitr::include_graphics("./figures/figure1.png")
```

To test the predictive and explanatory power of our model, we developed a world-learning paradigm in which we jointly manipulated the three information sources (Fig. 1). Children interacted on a tablet computer with a series of storybook speakers [@frank2016using]. The speakers used novel words (e.g., "wug") in the context of two potential referents. This situation is depicted in Fig. 1a iv, in which a speaker (here, a frog) appears with a known object (a duck, left) and an unfamiliar object (the diamond-shaped object, right). To identify the referent, the child could rely upon the three information sources described above. First, they may infer that a cooperative speaker would have used the word "duck" to refer to the known object (the duck); the fact that the speaker did not say duck then suggests that the speaker is most likely referring to a different object (the unfamiliar object). This basic inference is oftentimes referred to as a mutual exclusivity inference [@markman1988children; @halberda2003development]. More generally speaking, the listener can infer the referent of the novel word by assuming that the speaker is a rational agent who chooses the most informative words to refer to objects [@clark1987principle; @frank2014inferring]. Second, the child may rely upon what has already been established in the common ground with the speaker. Listeners expect speakers to communicate about things that are new to the common ground [@akhtar1996role; @diesendruck2004two]. Thus, the inference about the novel word referring to the unfamiliar object also depends on which object is new in context (Fig. 1a and b i-iii). Finally, the child may rely upon their previously acquired semantic knowledge, that is, how sure they are that the known object is called "duck". If the known object is something less familiar, such as a chess piece (e.g., a pawn), a 3-year-old child may draw a weaker inference, if they draw any inference at all [@lewis2020-me; @grassmann2015children]. Taken together, the child has the opportunity to integrate their assumptions about (1) cooperative communication, (2) their understanding of the common ground, and (3) their existing semantic knowledge. In some versions of the experiment, some of these information sources were aligned (Fig. 1a) but in some they were in conflict (Fig. 1b).

@@

We tested the model in its ability to predict children’s actual behavior - at an age (between 2 and 5 years) at which they learn language at an exponential rate [@bloom2002children]. We estimated children’s (N=148) developing sensitivity to individual information sources in separate experiments (Experiment 1 and 2) (see Fig. 1c-e). We then generated parameter-free, quantitative, *a priori* model predictions (developmental trajectories) representing the model's expectations about how children should behave in a new situation in which all three information sources had to be integrated. We generated model predictions for 24 experimental conditions: 12 objects of different familiarities (requiring different levels of semantic knowledge), with novelty either conflicting or coinciding; Fig. 1. We compared these predictions to newly collected data from N = 220 children from the same age range (Experiment 3).

The results showed a very close alignment between model predictions and the data across the entire age range. That is, the average developmental trajectories predicted by the model resembled the trajectories found in the data (Fig. S6). For a more quantitative analysis, we binned predictions and data by year and correlated them. We found a high correlation, with the model explaining 79% of the variance in the data (Fig. 2a). These results seem to support the assumptions in the model that children integrate all available information sources. However, it is still possible that simpler models might make equally good -- or even better -- predictions.

Thus, we formalized the alternative view that children selectively ignore information sources in the form of three lesioned models (Fig. 2b). These models assume that children follow the heuristic “ignore X” (with X being one of the information sources) when multiple information sources are presented together.

The *no word knowledge model* uses the same model architecture as the rational integration model. It takes in expectations about speaker informativeness and common ground, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge). That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge. The *no common ground model* takes in object specific semantic knowledge and speaker informativeness but ignores common ground information. Instead of assuming that one object has a higher prior probability to be the referent because it is new in context, the speaker thinks that both objects are equally likely to be the referent. As a consequence, the listener does not differentiate between situations in which common ground is aligned or in conflict with the other information sources. Finally, according to the *no speaker informativeness model*, the listener does not assume that the speaker is communicating in an informative way and hence ignores the information provided by the utterance. As a consequence, the inference is solely based on common ground expectations.

We found little support that children make inferences following one of the heuristic models (Fig. 2b). When using Bayesian model comparison via marginal likelihood of the data, [@lee2014bayesian], we find that the data was several orders of magnitude more likely under the rational integration model compared to any of the lesioned models (Fig. 2). Taken together, we may conclude that children considered all available information sources.

(ref:figlab2) **Predicting information integration**. Correlation between model predictions and child inference data for all 24 conditions and for each age group (binned by year) for the rational integration model (a) and the three lesioned models (b). Horizontal and vertical error bars show 95% HDI. Inset shows an example of model predictions as developmental trajectories (see Fig. 3). The no word knowledge model includes developmental change for overall vocabulary development but ignores the identity of the known object. The no common ground model assumes that children ignore information from common ground and the no speaker informativeness model assumes that children ignore inferences that are licensed by expectations about informative communication. BF~10~ gives the Bayes Factor in favor of the integration model based on the marginal likelihood of the data under each model.

@@

The fact that children integrated all the available information sources may be surprising, but does not rule out that the integration process itself might be different from the one described in the rational integration model, which assumes that all information sources enter into an integrated inference process. However, a more modular view seems equally plausible: children might compute separate inferences based on a subset of the available information and then integrate them by weighting them according to some ratio. This view would allow for the possibility that some information sources are considered to be more important than others. In other words, children might be biased towards some information sources. We formalized this alternative view as a *biased integration model*. This model assumes that semantic knowledge and expectations about speaker informativeness enter into one inference (mutual exclusivity inference [@markman1988children; @lewis2020-me; @clark1987principle]) while common ground information enters into a second one. The outcome of both processes are then weighted according to the parameter $\phi$. Like the rational integration model, this model takes in all available information sources in an age sensitive way and assumes that they are integrated - the only difference lies in the nature of the integration process.

The parameter $\phi$ in the biased integration model is unknown ahead of time and has to be estimated based on the experimental data. That is, in contrast to the rational integration model, the biased integration model does not allow to make *a priori* predictions about new data in the way we describe above. For the model comparison, we therefore constrained the parameters in the rational integration model by the data from EXperiment 3 as well. As a consequence, both models use all the information available to constrain their parameters (see Fig. S4).

@@

The biased integration model makes reasonable predictions that explain a large proportion of the variance in the data (Fig. 3b). The parameter $\phi$ - indicating the bias to one of the inferences - was estimated to favor the mutual exclusivity inference (mode = `r phi%>%pull(mode)`; 95% highest density interval (HDI): `r phi%>%pull(lci)` - `r phi%>%pull(uci)`, see Fig. 3d). However, the rational integration model presented a much better fit to the data, both in terms of correlation and marginal likelihood of the data (Fig. 3). Thus, a fully integrated - as opposed to a sequential and biased - integration process explained the data better.

The rational integration model assumes that the integration process itself does not change with age [@bohn2019pervasive]. That is, while children's sensitivity to each information source develops, the way they relate to one another remains the same. An alternative perspective would be to assume that the integration process itself changes with age. The biased integration model provides a way to think about developmental change in the integration process: Children are biased towards some information sources, but the bias itself changes with age. We formalize such an alternative view as a *developmental bias model* which is structurally identical to the biased integration model but in which the parameter $\phi$ changes with age. The model assumes that the importance of the different information sources changes with age.

@@

The developmental bias model also explains a substantial portion of the variance in the data (Fig. 3c). The estimated developmental trajectory for the bias parameter $\phi$ suggests that younger children put a higher emphasis on common ground information, while older children rely more on the mutual exclusivity inference (Fig. 3d). The relative importance of the two inferences seems to switch at around age 3. Yet again, when we directly compare the competitor models, we find that the data is several orders of magnitude more likely under the rational integration model (Fig. 3). Interestingly, when we compared the rational integration model with its parameters not constrained by the experimental data (i.e. the "pure" prediction model described above), it also outperformed both bias models (see Fig. S10 and Tab. S6). Taken together, these results show that the integration process is best described as fully integrated and stable over time.

(ref:figlab3) **Explaining information integration across development**. (a) Model predictions from the rational integration model (colored lines) next to the behavioral data (dotted black lines with 95% CI in gray) for all 24 experimental conditions. Top row (blue) shows conditions in which common ground information is congruent with speaker informativeness, bottom row (red) shows conditions in which they are incongruent. Known objects are ordered based on their rated age of acquisition (left to right). Light dots represent individual data points. (b) Correlations between model predictions binned by age and condition for the integration model and (c) the two mixture models. Vertical and horizontal error bars show 95% HDIs. BF~10~ gives the Bayes Factor in favor of the rational integration model based on the marginal likelihood of the data under each model. (d) Posterior distribution of the bias parameter in the biased integration model and developmental trajectories for the bias parameter in the developmental bias model based on 300 random draws from the posterior distribution of the intercept and slope.

>>>>

author: 
  - name          : "Manuel Bohn"
    affiliation   : "1,2,*"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "manuel_bohn@eva.mpg.de"
  - name          : "Michael Henry Tessler"
    affiliation   : "3,*"
  - name          : "Megan Merrick"
    affiliation   : "1"
  - name          : "Michael C. Frank"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"
  - id            : "2"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
  - id            : "3"
    institution   : "Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology"
  - id            : "*"
    institution   : "These authors contributed equally to this work"

abstract: |
  Before formal education begins, children typically acquire a vocabulary of thousands of words. This learning process requires the use of many different information sources in their social environment, including the context in which they hear words used and their current state of knowledge. How is this information integrated? We specify a developmental model according to which children consider information sources in an age-specific way and integrate them via Bayesian inference. This model accurately predicted 2-to-5 year-old children’s word learning across a range of experimental conditions. Model comparison suggests that the central locus of development is an increased sensitivity to individual information sources, rather than changes in  integration ability. This work presents a quantitative developmental theory of information integration during language learning, and illustrates how formal models can be used to make a quantitative test of the predictive and explanatory power of competing theories.

keywords          : "language acquisition, social cognition, pragmatics, Bayesian modeling, common ground"

@@

Human communicative abilities are unrivaled in the animal kingdom[@taylor2016language; @tomasello2008origins; @fitch2010evolution]. Language -- in whatever modality -- is the medium that allows humans to collaborate and coordinate in species-unique ways, making it the bedrock of human culture and society [@smith1997major]. Thus, to absorb the culture around them and become functioning members of society, children need to learn language [@tomasello2018natural]. A central problem in language learning is referent identification: To acquire the conventional symbolic relation between a word and an object, a child must determine the intended referent of the word. However, there is no unique cue to reference that can be used across all situations [@frank2013social]. Instead, referents can only be identified inferentially by reasoning about the speaker’s intentions [@bohn2019pervasive; @bruner1983child; @clark2009first; @tomasello2009constructing]. That is, the child has to infer what the speaker is communicating about based on information sources in the utterance’s social context.

From early in development, children use several different mechanisms to harness social-contextual information sources [@bohn2019pervasive; @clark2009first; @bloom2002children]. Children expect speakers to use novel words for unknown objects [@clark1987principle; @markman1988children; @carey1978acquiring; @halberda2003development], to talk about objects that are relevant [@frank2014inferring; @schulze20133], new in context [@akhtar1996role; @diesendruck2004two], or related to the ongoing conversation [@bohn_le_peloquin_koymen_frank_2020; @sullivan2016discourse; @horowitz2015young]. These different mechanisms, however, have been mainly described and theorized about in isolation. The picture of the learning process that emerges is that of a "bag of tricks": mechanisms that operate (and develop) independently from one another [@bloom2002children]. As such, this view of the learning process does not address the complexity of natural social interaction during which many sources of information are present [@bergelson2017nature; @frank2013social]. How do children arbitrate between these sources in order to accurately infer a speaker’s intention?

When information integration is studied directly, the focus is mostly on how children interpret an ambiguous referring expression in light of social-contextual information [@ganea2007infants; @graham2017words; @grosse201021; @jara2020social; @khu2020preschoolers; @matthews2006effect; @nilsen2009preschoolers; @kachel2021young]. In one classic study [@nadig2002evidence], children faced a 2 x 2 display with a ball, a pen and two glasses in it. The speaker, sitting on the opposite side of the display, saw only three of the four compartments: the ball, the pen, and one of the glasses. When the speaker asked for "the glass", children had to integrate the semantics of the utterance with the speaker’s perspective to correctly infer which of the glasses the speaker was referring to. This study advanced our understanding by documenting that preschoolers use both information sources, a finding confirmed by a variety of other work [@graham2017words; @khu2020preschoolers; @nilsen2009preschoolers]. Yet these studies do not specify -- or test -- the process by which children integrate different information sources. When interpreting their findings, work in this tradition refers to social-pragmatic theories of language use and learning [@grice1991studies; @sperber2001relevance; @clark1996using; @clark2009first; @tomasello2009constructing], all of which assume that information is integrated as part of a social inference process, but none of which clearly defines the process. As a consequence, we have no explicit and quantitative theory of how different information sources (and word learning mechanisms) are integrated.

We present a theory of this integration process. Following social-pragmatic theories of language learning [@clark2009first; @tomasello2009constructing], our theory is based on the following premises: information sources serve different functional roles but are combined as part of an integrated social inference process [@clark1996using; @grice1991studies; @shafto2012learning; @sperber2001relevance]. Children use all available information to make inferences about the intentions behind a speaker’s utterance, which then leads them to correctly identify referents in the world and learn conventional word–object mappings. We formalize the computational steps that underlie this inference process in a cognitive model [@frank2012predicting; @goodman2016pragmatic; @oberauer2019addressing]. In the remainder of this paper, we rigorously test this theory by asking how well it serves the two purposes of any psychological theory: prediction and explanation [@shmueli2010explain; @yarkoni2017choosing]. First, we use the model to make quantitative predictions about children’s behavior in new situations -- predictions we test against new data. This form of model testing has been successfully used with adults [@frank2012predicting; @lake2015human] and here we extend it to children. Next, we quantify how well the model explains the integration process by comparing it to alternative models that make different assumptions about *whether* information is integrated, *how* it is integrated, and how the integration process *develops.*

We focus on three information sources that play a central part in theorizing about language use and learning: (1) expectations that speakers communicate in a cooperative and informative manner [@frank2014inferring; @clark1987principle; @sperber2001relevance], (2) shared common ground about what is being talked about in conversation [@bohn2018common; @clark1996using; @clark2015common], and (3) semantic knowledge about previously learned word–object mappings [@fenson1994variability; @bloom2002children].

Our *rational integration model* arbitrates between information sources via Bayesian inference (see Fig. 1f for model formulae). A listener ($L_{1}$) reasons about the referent of a speaker’s ($S_{1}$) utterance. This reasoning is contextualized by the prior probability of each referent $\rho$ -- which we take to be a function of the common ground shared between the listener and the speaker. To decide between referents, the listener ($L_{1}$) reasons about what a rational speaker ($S_{1}$) with informativeness $\alpha$ would say given an intended referent. This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one. The informativity of each utterance is given by imagining which referent a listener, who interprets words according to their literal semantics (what we call a literal listener, $L_{0}$), would infer upon hearing the utterance. Naturally, this reasoning depends on what kind of semantic knowledge (for object j) $\theta$~j~ the speaker ascribes to the (literal) listener.

Taken together, this model provides a quantitative theory of information integration during language learning. The three information sources operate on different timescales: speaker informativeness is a momentary expectation about a particular utterance, common ground grows over the course of a conversation, and semantic knowledge is learned across development. This interplay of timescales has been hypothesized to be an important component of word meaning inference [@frank2009using; @mcmurray2012word], and we link these different time-dependent processes together via their hypothesized impact on model components. Furthermore, the model presents an explicit and substantive theory of development. It assumes that, while children’s sensitivity to the individual information sources increases with age, the way integration proceeds remains constant [@bohn2019pervasive; @bohn_tessler_merrick_frank_2019]. In the model, this is accomplished by creating age-dependent parameters capturing developmental changes in sensitivity to speaker informativeness ($\alpha$~i~, Fig. 1d), the common ground ($\rho$~i~, Fig. 1c), and object specific semantic knowledge ($\theta$~i,j~, Fig. 1e).

```{r fig1, include = T, fig.align = "center", fig.cap = "Experimental task and model. (a and b) Screenshots from the experimental task. (i) The speaker encounters one object and then leaves the scene (ii). While the speaker is away, a second object appears (iii), when returning, the speaker uses a novel word to request an object (iv). Sections (i) to (iii) establish common ground between the speaker and the listener, in that one object is new in context (green). The request in (iv) licenses an inference based on expectations about how informative speakers are (red). Listeners’ semantic knowledge enters the task because the identity of the known object on one of the tables is varied from well-known objects like a duck to relatively unfamiliar objects like a chess pawn (total of 12 objects -- blue). (a) shows the version of the experiment in which common ground information is congruent (i.e., point to the same object) with speaker informativeness and (b) shows the incongruent condition. The congruent and incongruent conditions are each paired with the 12 known objects, resulting in 24 unique conditions. (c to e) show developmental trajectories for each information source, estimated from separate experiments (see supplement). (f) gives the model equation for the rational integration model and links information sources to model parameters.", out.width="100%"}
knitr::include_graphics("./figures/figure1.png")
```

To test the predictive and explanatory power of our model we designed a world-learning experiment in which we jointly manipulated the three information sources (Fig. 1). Children interacted on a tablet computer with a series of storybook speakers [@frank2016using]. This situation is depicted in Fig. 1a iv, in which a speaker (here, a frog) appears with a known object (a duck, left) and an unfamiliar object (the diamond-shaped object, right). The speakers used a novel word (e.g., "wug") in the context of two potential referents, and then the child was asked to identify a new instance of the novel word, testing their inference about the speaker’s intended referent. To vary the strength of the child’s inference, we systematically manipulated the familiarity of the known object (from e.g., the highly familiar "duck" to the relatively unfamiliar "pawn") and whether the familiar or novel object was new to the speaker (meaning that it was not part of common ground).

This paradigm allows us to examine the integration of the three information sources described above. First, the child may infer that a cooperative and informative speaker [@clark1987principle; @frank2014inferring] would have used the word "duck" to refer to the known object (the duck); the fact that the speaker did not say "duck" then suggests that the speaker is most likely referring to a different object (the unfamiliar object). This basic inference is oftentimes referred to as a mutual exclusivity inference [@markman1988children; @halberda2003development]. Second, the child may draw upon what has already been established in the common ground with the speaker. Listeners expect speakers to communicate about things that are new to the common ground [@akhtar1996role; @diesendruck2004two]. Thus, the inference about the novel word referring to the unfamiliar object also depends on which object is new in context (Fig. 1a and b i-iii). Finally, the child may use their previously acquired semantic knowledge, that is, how sure they are that the known object is called "duck". If the known object is something less familiar, such as a chess piece (e.g., a pawn), a 3-year-old child may draw a weaker inference, if they draw any inference at all [@lewis2020-me; @grassmann2015children; @ohmerreinforcement]. Taken together, the child has the opportunity to integrate their assumptions about (1) cooperative communication, (2) their understanding of the common ground, and (3) their existing semantic knowledge. In one condition of the experiment, information sources were aligned (Fig. 1a) while in the other they were in conflict (Fig. 1b).

@@

We tested the model in its ability to predict 2 - 5 year-old children’s judgments about word meaning. We estimated children’s (N=148) developing sensitivity to individual information sources in two separate experiments (Experiments 1 and 2; see Fig. 1c-e). We then generated parameter-free *a priori* model predictions (developmental trajectories) representing the model’s expectations about how children should behave in a new situation in which all three information sources had to be integrated. We generated predictions for 24 experimental conditions: 12 objects of different familiarities (requiring different levels of semantic knowledge), with novelty either conflicting or coinciding; Fig. 1. We compared these predictions to newly collected data from N = 220 children from the same age range (Experiment 3). All procedures, sample sizes and analysis were pre-registered (see methods).

The results showed a very close alignment between model predictions and the data across the entire age range. That is, the average developmental trajectories predicted by the model resembled the trajectories found in the data (Fig. S6). For a more quantitative analysis, we binned predictions and data by child age (in years) and correlated the two. We found a high correlation, with the model explaining 79% of the variance in the data (Fig. 2a). These results support the assumption of the model that children integrate three all available information sources. However, it is still possible that simpler models might make equally good – or even better – predictions.

Thus, we formalized the alternative view that children selectively ignore information sources in the form of three lesioned models (Fig. 2b). These models assume that children follow the heuristic "ignore $x$" (with $x$ being one of the information sources) when multiple information sources are presented together.

The no *word knowledge model* uses the same model architecture as the rational integration model. It uses expectations about speaker informativeness and common ground but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge). That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age-specific average semantic knowledge. The *no common ground model* takes in object-specific semantic knowledge and speaker informativeness but ignores common ground information. Instead of assuming that one object has a higher prior probability to be the referent because it is new in context, the speaker thinks that both objects are equally likely to be the referent. As a consequence, the listener does not differentiate between situations in which common ground is aligned or in conflict with the other information sources. Finally, according to the *no speaker informativeness model*, the listener does not assume that the speaker is communicating in an informative way and hence ignores the utterance. As a consequence, the inference is solely based on common ground expectations.

We found little support for these heuristic models (Fig. 2b). When using Bayesian model comparison via marginal likelihood of the data [@lee2014bayesian], we find that the data was several orders of magnitude more likely under the rational integration model compared to any of the lesioned models (Fig. 2). Figure 2c exemplifies the differences between the models: all heuristic models systematically underestimate children’s performance in the congruent condition. Thus, even when the information sources are redundant (i.e. they all point to the same referent), children’s inferences are notably strengthened by each of them. In the incongruent condition, the no word knowledge model underestimates performance, because it does not differentiate between the different familiar objects, and in the case of a highly familiar word such as duck, underestimates the strength of the mutual exclusivity inference and its compensatory effect. The no speaker informativeness completely ignores this inferences, which leads to even worse predictions. On the contrary, the no common ground model overestimates performance because it ignores the dampening effect of common ground pointing to a different referent. Taken together, we conclude that children considered all available information sources.

(ref:figlab2) **Predicting information integration**. Correlation between model predictions and child inference data for all 24 conditions and for each age group (binned by year) for the rational integration model (a) and the three lesioned models (b). Horizontal and vertical error bars show 95% HDI. Inset shows an example of model predictions as developmental trajectories (see Fig. 3). BF~10~ gives the Bayes Factor in favor of the integration model based on the marginal likelihood of the data under each model. (c) Predictions from all models considered alongside the data (with 95% HDI) for two experimental conditions (familiar word: *duck*).

@@

In the previous section, we established that children integrated all available information sources. This result, however, does not speak to the process by which information is assumed to be integrated. Thus, in this section, we ask which integration process best explains children’s behavior.

The rational integration model assumes that all information sources enter into a joint inference process, but alternative integration processes are conceivable and might be consistent with the data. For example, the "bag of tricks" [@bloom2002children] hypothesis mentioned in the introduction could be re-phrased as a modular integration process: children might compute independent inferences based on subsets of the available information and then integrate them in a post-hoc manner by weighting them according to some parameter. This view would allow for the possibility that some information sources are considered to be more important than others. In other words, children might be biased towards some information sources. We formalized this alternative view as a *biased integration model*. This model assumes that semantic knowledge and expectations about speaker informativeness enter into one inference (mutual exclusivity inference [@markman1988children; @lewis2020-me; @clark1987principle]) while common ground information enters into a second one. The outcomes of both processes are then weighted according to the parameter $\phi$. Like the rational integration model, this model takes in all available information sources in an age-sensitive way and assumes that they are integrated. The only difference lies in the nature of the integration process: the biased integration model privileges some information sources of others in an ad-hoc manner.

The parameter $\phi$ in the biased integration model is unknown ahead of time and has to be estimated based on the experimental data. That is, in contrast to the rational integration model, the biased integration model has an additional degree of freedom which does not allow us to make *a priori* predictions about new data in the way we describe above. For a fair comparison, we therefore constrained the parameters in the rational integration model by the data from Experiment 3 as well. As a consequence, both models use all the data available to constrain their parameters (see Fig. S4).

@@

The biased integration model makes reasonable predictions and explains 78% of the variance in the data (Fig. 3b). The parameter $\phi$ -- indicating the bias to one of the inferences -- was estimated to favor the mutual exclusivity inference (Maximum A-Posteriori estimate = `r phi%>%pull(mode)`; 95% highest density interval (HDI): `r phi%>%pull(lci)` - `r phi%>%pull(uci)`, see Fig. 3d). However, the rational integration model presented a much better fit to the data, both in terms of correlation and the marginal likelihood of the data (Fig. 3). Figure 3e exemplifies the difference between the models: the biased integration model puts extra weight on the mutual exclusivity inference and thus fails to capture performance when this inference is weak compared to the common ground inference -- such as in the congruent condition for younger children. Thus, a fully integrated -- as opposed to a modular and biased -- integration process explained the data better.

The rational integration model assumes that the integration process itself does not change with age [@bohn2019pervasive]. That is, while children’s sensitivity to each information source develops, the way they relate to one another remains the same. The biased integration model provides an alternative proposal about developmental change, one in which the integration process itself changes with age. That is, children may be biased towards some information sources, and that bias itself may change with age. We formalize such an alternative view as a *developmental bias model* which is structurally identical to the biased integration model but in which the parameter $\phi$ changes with age. The model assumes that the importance of the different information sources changes with age.

@@

The developmental bias model also explains a substantial portion of the variance in the data: 78% (Fig. 3c). The estimated developmental trajectory for the bias parameter $\phi$ suggests that younger children put a stronger emphasis on common ground information, while older children rely more on the mutual exclusivity inference (Fig. 3d). The relative importance of the two inferences seems to switch at around age 3. Yet again, when we directly compare the competitor models, we find that the data is several orders of magnitude more likely under the rational integration model (Fig. 3). Looking at Figure 3e, we can see that the developmental bias model tends to underestimate children’s performance because the supportive interplay between the different inferences is constrained.

Finally, when we compared the rational integration model with its parameters not constrained by the experimental data (i.e. the "pure" prediction model described above), it also outperformed both bias models (see Fig. S10 and Tab. S6). Taken together, these results show that the integration process is best described as fully integrated and stable over time.

(ref:figlab3) **Explaining information integration across development**. (a) Model predictions from the rational integration model (colored lines) next to the behavioral data (dotted black lines with 95% CI in gray) for all 24 experimental conditions. Top row (blue) shows congruent conditions, bottom row (red) shows incongruent conditions. Familiar objects are ordered based on their rated age of acquisition (left to right). Light dots represent individual data points. (b) Correlations between model predictions binned by age and condition for the integration model and (c) the two biased models. Vertical and horizontal error bars show 95% HDIs. BF~10~ gives the Bayes Factor in favor of the rational integration model based on the marginal likelihood of the data under each model. (d) Posterior distribution of the bias parameter in the biased integration model and developmental trajectories for the bias parameter in the developmental bias model (e) Predictions from all models considered alongside the data (with 95% HDI) for two experimental conditions (familiar word: duck).
